An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 indicators/paper/paper.tex
Authorship fixes
Remove old aff letters
Author contributions

% Middle authors
\author[d]{Sumit Agrawal} 
\author[e]{Wael Al Saeed} 
\author[f]{Taylor Arnold} 
\author[g]{Amartya Basu}
\author[h]{Jacob Bien} 
\author[i]{{\'A}ngel A. Cabrera} 
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[d]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[d]{David C. Farrow}
\author[i]{Jodi Forlizzi}
\author[d]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[i]{Robin Han}
\author[d]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[d]{Raphael Hyde}
\author[h]{Sangwon Hyun}
\author[e]{Ananya Joshi}
\author[j]{Jimi Kim}
\author[i]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[i]{Yeon Jin Lee}
\author[k]{Kenneth Lee} 
\author[b]{Zachary C. Lipton}
\author[i]{Michael X. Liu}
\author[l]{Lester Mackey} 
\author[b]{Kathryn Mazaitis}
\author[m]{Daniel J. McDonald} 
\author[d]{Phillip McGuinness}
\author[n,o]{Balasubramanian Narasimhan} 
\author[d]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[i]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[o]{Samyak Rajanala}
\author[e]{Dawn Rucker}
\author[d]{Chris Scott}
\author[p]{Nigam Shah} %s
\author[q]{Vishnu Shankar} %n
\author[k]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[r]{Noah Simon} %q
\author[d]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[k]{Shiyu Tan}
\author[n,o]{Robert Tibshirani}
\author[n]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a,b]{Larry Wasserman}
\author[d]{Benjamin Weaver}
\author[s]{Jeremy C. Weiss} %m
\author[d]{Spencer Whitman}
\author[i]{Kristin Williams}

@@

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: areinhar@stat.cmu.edu} 
\equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
  to this work.}

>>>>

% Middle authors
\author[d]{Sumit Agrawal}
\author[e]{Wael Al Saeed}
\author[f]{Taylor Arnold}
\author[g]{Amartya Basu}
\author[h]{Jacob Bien}
\author[i]{{\'A}ngel A. Cabrera}
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[d]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[d]{David C. Farrow}
\author[i]{Jodi Forlizzi}
\author[d]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[b]{George Haff}
\author[i]{Robin Han}
\author[d]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[d]{Raphael Hyde}
\author[h]{Sangwon Hyun}
\author[e]{Ananya Joshi}
\author[j]{Jimi Kim}
\author[i]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[i]{Yeon Jin Lee}
\author[k]{Kenneth Lee}
\author[b]{Zachary C. Lipton}
\author[i]{Michael X. Liu}
\author[l]{Lester Mackey}
\author[b]{Kathryn Mazaitis}
\author[m]{Daniel J. McDonald}
\author[d]{Phillip McGuinness}
\author[n,o]{Balasubramanian Narasimhan}
\author[d]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[i]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[n]{Samyak Rajanala}
\author[e]{Dawn Rucker}
\author[d]{Chris Scott}
\author[p]{Nigam H. Shah} 
\author[q]{Vishnu Shankar} 
\author[k]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[r]{Noah Simon} 
\author[d]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[m]{Shuyi Tan}
\author[n,o]{Robert Tibshirani}
\author[n]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a,b]{Larry Wasserman}
\author[d]{Benjamin Weaver}
\author[s]{Jeremy C. Weiss} 
\author[d]{Spencer Whitman}
\author[i]{Kristin Williams}

@@

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Author contributions: A.R., L.B., M.J., A.R., J.T., A.C,
  E.J.C., N.D., D.C.F, A.J.H., S.H., M.J., J.K., W.L.M.K, Z.C.L., L.M., N.L.O.,
  J.C.W, R.R., and R.J.T., obtained and managed data;
  A.R., J.B., J.F., Z.C.L., L.M., D.J.M., A.P., S.R., D.R., C.S. N.S., R.T.,
  V.V., L.W., B.W., J.C.W, S.W., R.R., and R.J.T. designed software and
  research,
  A.R., L.B., M.J., A.R., J.T., W.A.S., T.A., A.B., J.B., L.B., A.A.C., A.C.,
  E.J.C., B.C., S.C., N.D., D.C.F., J.G., S.G., A.G., G.H., R.H., K.H., A.J.H.,
  S.H., M.J., A.J., J.K., A.K., M.X.L., L.M., K.M., D.J.M., B.N., M.P.O.,
  N.L.O., P.P., C.A.P., S.R., C.S., V.S, J.S, D.S., N.S., B.Y.S., V.S., S.T.,
  J.T., R.T., J.C.W, and R.J.T. developed software;
  S.A., W.A.S., A.C., B.C., D.C.F., S.G., G.H., K.M., D.J.M., B.N., C.S., J.S.,
  D.S., B.Y.S., A.K.V.N. managed technical infrastructure and systems;
  A.R., L.B., M.J., A.R., J.T, J.B., A.C., E.J.C., N.D., D.C.F., A.G., K.H.,
  A.J.H., R.H., S.H., A.J., J.K., K.L., Y.J.L, Z.C.L., L.M., D.J.M., P.M., B.N.,
  N.L.O., P.P., C.A.P., S.R., N.S., V.S., J.S., D.S., N.S., S.T., J.T., R.T.,
  V.V., L.W., J.C.W., R.R., and R.J.T. performed research;
  and A.R., L.B., M.J., A.R., J.T., and R.J.T. wrote the paper.
}
\authordeclaration{No competing interests to declare.}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be
  addressed. E-mail: areinhar@stat.cmu.edu}
\equalauthors{\textsuperscript{2}L.B., M.J., A.R., and J.T. contributed equally
  to this work.}
